Adaptive Approximation for Multivariate Linear Problems \\ with Inputs Lying in a Cone

### 2018-11-04 RICAM2018NovTalk.tex

\begin{frame}
\frametitle{Example Bases}
\vspace{-3ex}
	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_0.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_3.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_4.png} 
	\tabularnewline[-7ex]
	Legendre
	\tabularnewline
	\tabularnewline
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_3.png} 
\tabularnewline[0ex]
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_0.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_4.png} 
\tabularnewline[-7ex]
Chebyshev \tabularnewline
\tabularnewline
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_3.png} 
	\end{tabular}
\end{frame}

@@

\begin{frame}
\frametitle{Complex Exponential and Walsh Bases}
\vspace{-3ex}
	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_0.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_3.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_4.png} 
	\tabularnewline[-7ex]
	Cosine \& Sine
	\tabularnewline
	\tabularnewline
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_3.png} 
\tabularnewline[0ex]
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_0.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_4.png} 
\tabularnewline[-7ex]
Walsh \tabularnewline
\tabularnewline
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_3.png} 
	\end{tabular}
\end{frame}

@@

\begin{frame}{Cones of Integrands \footfullcite{HicJim16a,JimHic16a}}

@@

\begin{align*}
n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}\\
	 \sigma_k(f) & = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \qquad  \hsigma_{\ell,k}(f)  = \sum_{i=n_{\ell-1}+1}^{n_\ell}  \sum_{m=1}^{\infty} \bigabs{\hf(\vj_{i+mn_{k}})},\\
	 \cc &: = \left\{f \in \cf :  \sigma_k(f) \le a b^{k - \ell}\sigma_\ell(f), \   \hsigma_{\ell,k}(f) \le \sigma_k(f) \right\} \\
      &\begin{array}{l}\Sapp(f,n_k) = \frac 1{n_k} \sum_{i=1}^{n_k} f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
    \end{array}
\end{align*}

@@

\begin{frame}{Asian Option Pricing}
\end{frame}

@@

>>>>

@@

\begin{frame}{Complex Exponential and Walsh Bases}
\vspace{-3ex}
	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_0.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_3.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_4.png} 
	\tabularnewline[-7ex]
	Cosine \& Sine
	\tabularnewline
	\tabularnewline
		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_3.png} 
\tabularnewline[0ex]
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_0.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_4.png} 
\tabularnewline[-7ex]
Walsh \tabularnewline
\tabularnewline
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_3.png} 
	\end{tabular}
\end{frame}

@@

\begin{frame}{Cones of Integrands Whose Fourier Coefficients Decay Steadily\footfullcite{HicJim16a,JimHic16a}}

@@

\begin{align*}
n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}, \quad \text{true coef.} = \tf(\vj) \approx \tf_{\text{disc}}(\vj) = \text{discrete coef.}\\
	 \sigma_k(f) & = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad  \hsigma_{k,\ell}(f)  = \sum_{i=n_{k-1}+1}^{n_k} \sum_{m=1}^{\infty} \bigabs{\hf(\vj_{i+mn_{\ell}})}, \quad \sigma_{\textup{disc},k}(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf_{\text{disc}}(\vj_i)} \\
	 \cc &: = \left\{f \in \cf :  
	 \sigma_\ell(f) \le a_1 b_1^{\ell - k}\sigma_k(f), \   \hsigma_{k,\ell}(f) \le a_2 b_2^{\ell - k} \sigma_\ell(f) \quad \forall k \le \ell \right\} \quad a_1, a_2 > 1 > b_1, b_2\\
      &\begin{array}{l}\Sapp(f,n_k) = \frac 1{n_k} \sum_{i=1}^{n_k} f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)} \le C(k) \sigma_{\textup{disc},k}(f)
    \end{array}
\end{align*}

\begin{frame}{ Option Pricing\footfullcite{ChoEtal17b}}
\vspace{-12ex}
\begin{tabular}{m{11cm}m{2.5cm}}
	\[
	\begin{aligned}
	 \text{fair price} = 
	\int_{\reals^d}\me^{-r T}\max\left(\frac{1}{d}\sum_{j=1}^d S_{j}-K, 0\right) 
	\frac{\me^{-\vz^T\vz/2}}{(2\pi)^{d/2}}\,\dif \vz \approx \$13.12
	\end{aligned}
	\]
	& 
	\financePict
\end{tabular}
\vspace{-4ex}
\begin{gather*}
S_{j} =  S_0\me^{(r-\sigma^2/2)jT/d+\sigma x_j} = \text{stock price at time } 
jT/d, \\
\vx  = \mA \vz, \quad \mA \mA^T = \mSigma = \Bigl ( \min(i,j) T/d \Bigr) _{i,j = 1}^d,
\quad T = 1/4, \ d=13 \text{ here}
\end{gather*}
\begin{equation*}
\begin{array}{cccccccc}
\text{Error}& && \text{Median}&& \text{Worst 10\%} & \text{Worst 10\%} \\
\text{Tolerance} & \multicolumn{2}{c}{\text{Method}}  & \text{Error} & \text{Accuracy} 
& n & \text{Time (s)} \\
\toprule
\input{ProgramsImages/AsianOutput.txt}
\end{array}
\end{equation*}
\vspace{-8ex}

@@

@@

\begin{frame}{Example Bases for Function Approximation}
\vspace{-3ex}
	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_0.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_3.png}  &
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_4.png} 
	\tabularnewline[-7ex]
	Legendre
	\tabularnewline
	\tabularnewline
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_3.png} 
\tabularnewline[0ex]
		\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_0.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_4.png} 
\tabularnewline[-7ex]
Chebyshev \tabularnewline
\tabularnewline
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_1.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_3.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_2.png}  &
\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_3.png} 
	\end{tabular}
\end{frame}
